Case Study: ChIP-seq Differential Peak Calling (csaw)

### 2018-07-06 datasets/ChIP-seq/ChIPseq-h3k4me3-csaw.Rmd
Update covariate plot title for random covariate

```{r, rand-diag-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(res_df, pvalue = "PValue", covariate = "uninf_covar") +
    ggtitle("Region width as independent covariate") +
    xlab("Region Width")
```

>>>>

```{r, rand-diag-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(res_df, pvalue = "PValue", covariate = "uninf_covar") +
    ggtitle("Random independent covariate") +
    xlab("Region Width")
```
